### 2024-02-20 cv/cv-body.tex
Add paper
space
Update publications

\begin{description}
\tightlist
\item[2022]
\textbf{Anderson, S.C.}, E.J. Ward, P.A. English, L.A.K. Barnett.
sdmTMB: an R package for fast, flexible, and user-friendly generalized
linear mixed effects models with spatial and spatiotemporal random
fields. bioRxiv 2022.03.24.485545.
\url{https://doi.org/10.1101/2022.03.24.485545}.
\item[2021]
\textbf{Anderson, S.C}, B.M. Connors, P.A. English, R.E. Forrest, R.
Haigh, K.R. Holt. Trends in Pacific Canadian groundfish stock status.
bioRxiv 2021.12.13.472502.
\url{https://doi.org/10.1101/2021.12.13.472502}.
\end{description}

@@

@@

evaluation. In press at Can. J. Fish. Aquat. Sci.

@@

@@

standardization under reduced survey coverage. In press at ICES Journal
of Marine Science. \url{https://doi.org/10.1093/icesjms/fsad155}.

@@

receive more attention when named after celebrities? In press at
Conservation Biology. \url{https://doi.org/10.1111/cobi.14184}.

@@

Journal of Marine Science. In press.

@@

Fisheries. In press. \url{https://doi.org/10.1111/faf.12753}.

>>>>

\begin{description}
\tightlist
\item[2024]
Thorson, J.T., \textbf{S.C. Anderson}, P. Goddard, C.N. Rooper.
tinyVAST: R package with an expressive interface to specify lagged and
simultaneous effects in multivariate spatio-temporal models. arXiv.
\url{https://doi.org/10.48550/arXiv.2401.10193}.
\item[2022]
\textbf{Anderson, S.C.}, E.J. Ward, P.A. English, L.A.K. Barnett, J.T.
Thorson. sdmTMB: an R package for fast, flexible, and user-friendly
generalized linear mixed effects models with spatial and spatiotemporal
random fields. bioRxiv 2022.03.24.485545.
\url{https://doi.org/10.1101/2022.03.24.485545}.
\item[2021]
\textbf{Anderson, S.C}, B.M. Connors, P.A. English, R.E. Forrest, R.
Haigh, K.R. Holt. Trends in Pacific Canadian groundfish stock status.
bioRxiv 2021.12.13.472502.
\url{https://doi.org/10.1101/2021.12.13.472502}.
\end{description}

@@

\item[2024]
\textbf{Anderson, S.C.}, P.A. English, K.S.P. Gale, D.R. Haggarty, C.K.
Robb, E.M. Rubidge, P.L. Thompson. Impacts on population indices if
scientific surveys are excluded from marine protected areas. ICES
Journal of Marine Science. fsae009.
\url{https://doi.org/10.1093/icesjms/fsae009}.
\item[2024]
Hughes, B.B., Beheshti, K.M., Tinker, M.T., Angelini, C., Endris, C.,
Murai, L., \textbf{Anderson, S.C.}, Espinosa, S., Staedler, M.,
Tomoleoni, J.A., Sanchez, M., and Silliman, B.R. Top-predator recovery
abates geomorphic decline of a coastal ecosystem. Nature 626(7997):
111--118. \url{https://doi.org/10.1038/s41586-023-06959-9}.
\item[2024]
English, P.A., C.M. Picco, J.C. Edwards, D.R. Haggarty, R.E. Forrest,
\textbf{S.C. Anderson}. Spatial restrictions hinder avoidance of choke
species in an Indigenous rights-based fishery. People and Nature. 6:
75--90. \url{https://doi.org/10.1002/pan3.10554}.

@@

evaluation. Can. J. Fish. Aquat. Sci. 80(12): 1869-1889.

@@

\item[2024]

@@

standardization under reduced survey coverage. ICES Journal of Marine
Science. 80(9): 2368--2379.
\url{https://doi.org/10.1093/icesjms/fsad155}.

@@

receive more attention when named after celebrities? Conservation
Biology. e14184. \url{https://doi.org/10.1111/cobi.14184}.

@@

Journal of Marine Science. 80(5): 1539--1550.

@@

Fisheries. 24: 652--674. \url{https://doi.org/10.1111/faf.12753}.
